Results_paper1

### 2019-04-27 Paper1_results.Rmd
working_bits

library(tidyverse)
library(plyr)
library(lubridate)
library(ggpubr)
library(zoo)
library(lubridate)
library(FNN)
library(forecast)
library(astrochron)
library(WaveletComp)
library(data.table)
library(heatwaveR)
library(viridis)
library(ggrepel)
library(plyr)
library(maptools)
library(sp)
library(geosphere)
# library(marmap)
library(PBSmapping)
library(scales)
library(grid)
library(gridExtra)
library(circular)
library(fossil)
library(mapproj)
# library(rgeos)
library(ncdf4)
# library(sinkr)
library(spacetime)
library(reshape2)
library(plyr) # Never load plyr when also loading the tidyverse. It causes a lot of conflicts.
library(stringr)
library(doMC); doMC::registerDoMC(cores = 4)
library(fasttime)

@@

## Functions
source("functions/earthdist.R")
source("functions/wind.rose.R")
```

@@

Loading in the matched satellite temperature data

@@

@@

SACTN_fyears <- filtered_years(df = SACTN_overlap) 
MUR_fyears <- filtered_years(df = insitu_MUR) 
OISST_fyears <- filtered_years(df = insitu_OISST) 
G1SST_fyears <- filtered_years(df = insitu_G1SST) 
K10_fyears <- filtered_years(df = insitu_K10) 
```

@@

```{r}
load("Data_P1/site_list_sub.Rdata")
west <- site_list_sub
west$coast <- "west" # Chnages wc to west

@@

## Create a visualisation of the sites at the different distances from the coastline
****Fix: Fill to show the temperature variation at Benguela coast| also fix the site names*

load("Data_P1/south_africa_coast.RData")
load("Data_P1/bathy/sa_bathy.RData")
load("Data_P1/bathy/bathy.RData")
names(south_africa_coast)[1] <- "lon"

@@

# Define plotting parameters
sa_lats <- c(-37, -27); sa_lons <- c(14, 34)

 plot1 <- ggplot() +#coord_equal() + 
  geom_raster(data = sa_bathy, aes(x = lon, y = lat, fill = depth)) +
  #geom_raster(data = isobath200, aes(x = lon, y = lat, fill = coast)) +
  stat_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth, alpha = ..level..), 
               colour = "black", size = 0.2, binwidth = 200, na.rm = TRUE, show_guide = FALSE) +
  geom_polygon(data = south_africa_coast, aes(x = lon, y = lat, group = group), 
               size = 0.5, colour = "black", fill = "white") +
  #geom_path(data = sa_provinces_new, aes(x = long, y = lat, group = group)) +
  # geom_polygon(data = wcBox, aes(x = lon, y = lat, group = group), alpha = 0.20, 
  #              colour = "bisque1", fill = "bisque1") +
  geom_point(data = site_list_sub, aes(x = lon, y = lat), alpha = 0.8, size = 1.6) +
  geom_point(data = site_pixels, aes(x = lon, y = lat), colour = "white", shape = 0, alpha = 0.8, size = 2.1) +
  geom_rect(data = bbox, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), 
            alpha = 0.4, colour = "red", size = 0.1, linetype = 1) +
  scale_alpha_continuous(breaks = c(-200, -1000, -2000, -3000, -4000, -5000),
                         guide_legend(title = "depth (m)")) +
  scale_fill_gradient(low = "dodgerblue4", high = "dodgerblue", na.value = "steelblue4", 
                      breaks = c(-1000, -2000, -3000, -4000, -5000),
                      guide_legend(title = "depth (m)")) +
  labs(title = NULL, x = NULL, y = NULL) +
  guides(colour = guide_legend(override.aes = list(size = 3))) +
  #guide_legend(ncol = 2) +
  theme(legend.key = element_rect(colour = NA, size = 0.2),
        legend.key.height = unit(0.4, "cm"),
        legend.background = element_blank()) +
        #legend.justification = c(1,0), legend.position = c(0.5, 0.4)) +
  coord_cartesian(xlim = sa_lons, ylim = sa_lats)
 plot1

 # Added in the bathy data but this is not needed for any of the analyses.
 # This just shows the bounding boxes 
```

@@

@@

```{r}
load("Data_P1/SACTN_overlap.RData")
load("Data_P1/wind_daily.RData")
wind_daily <- wind_daily%>% 
  dplyr::rename(site = temp_sites) # Renaming to match the `match_func` previously created

insitu_wind <- match_func(df = wind_daily)  # Using `match_func`

insitu_wind <- insitu_wind %>% 
  filter(year(date) %in% seq(2010, 2014)) # The years 2010-2014 is the years of interest and the years for which wavelets are/will be created.

@@

wave_daily_renamed <- insitu_wind %>% 
  dplyr::rename(spd = mean_speed) %>%
  dplyr::rename(dir = dir_circ) 
source("functions/wind.rose.R")
p.wr2 <- plot.windrose(data = wave_daily_renamed,
              spd = "spd",
              dir = "dir")
p.wr3 <- p.wr2 + facet_wrap(.~ site, ncol = 2, nrow = "") +
  theme(strip.text.x = element_text(size = 25))
p.wr3 # RWS: You'll want to remove the NA part in the figure output
```

@@

# MODIS_Chloro <- "~/Documents/Masters_2019/MastersProject/Data"
# MODIS_Chloro <- fread(paste0(MODIS_Chloro, "/BC-MODIS.Aqua.L3m_8D_CHL_chlor_a_9km-2002185-2018345.csv"),
#             col.names = c("lon", "lat", "chloro", "date"))

@@

To do list:
- fix wind roses
- fix chloro
- Robs pixels
- EOFs
- fix pca

@@

PCA_1 <- rda(tester)
summary(PCA)

@@

>>>>

library(tidyverse)
library(plyr)
library(lubridate)
library(ggpubr)
library(zoo)
library(lubridate)
library(FNN)
library(forecast)
library(astrochron)
library(WaveletComp)
library(data.table)
library(heatwaveR)
library(viridis)
library(ggrepel)
library(plyr)
library(maptools)
library(sp)
library(geosphere)
library(PBSmapping)
library(scales)
library(grid)
library(gridExtra)
library(circular)
library(fossil)
library(mapproj)
library(ncdf4)
library(reshape2)
library(plyr) # Never load plyr when also loading the tidyverse. It causes a lot of conflicts.
library(stringr)
library(doMC); doMC::registerDoMC(cores = 4)
library(fasttime)
library(xtable)

@@

## Functions
source("functions/earthdist.R")
source("functions/wind.rose.R")
source("functions/theme.R")
source("functions/scale.bar.func.R")
```

@@

@@

## Loading in the matched satellite temperature data

@@

SACTN_fyears <- filtered_years(df = SACTN_overlap) 
MUR_fyears <- filtered_years(df = insitu_MUR) 
OISST_fyears <- filtered_years(df = insitu_OISST) 
G1SST_fyears <- filtered_years(df = insitu_G1SST) 
K10_fyears <- filtered_years(df = insitu_K10)

# save(SACTN_fyears, file = "Data_P1/SACTN_fyears.RData")
# save(MUR_fyears, file = "Data_P1/MUR_fyears.RData")
# save(OISST_fyears, file = "Data_P1/OISST_fyears.RData")
# save(G1SST_fyears, file = "Data_P1/G1SST_fyears.RData")
# save(K10_fyears, file = "Data_P1/K10_fyears.RData")
```

@@

```{r}
load("Data_P1/site_list_sub.Rdata")
xtable(site_list_sub, auto = TRUE)
west <- site_list_sub
west$coast <- "west" # Chnages wc to west

@@

## Create a visualisation of the sites at the different distances from the coastline

```{r}
load("Data_P1/south_africa_coast.RData")
load("Data_P1/bathy/sa_bathy.RData")
load("Data_P1/bathy/bathy.RData")
load("Data_P1/site_list_sub.Rdata")
load("Data_P1/site_pixels.RData")
load("Data_P1/MUR.RData")
names(south_africa_coast)[1] <- "lon"

@@

# Setting up the theme
theme_set(theme_bw())
limits <- c(12,28) # for colour bar
#breaks <- seq(6, 30, 2) # Create breaks to be used for colour bar

# Define plotting parameters
sa_lats <- c(-37, -27); sa_lons <- c(14, 50)

site_map <- ggplot(data = south_africa_coast, aes(x = lon, y = lat)) + bw_update +
  geom_raster(data = MUR, aes(x = lon, y = lat, fill = temp)) +
   geom_polygon(data = south_africa_coast, aes(x = lon, y = lat, group = group),
                fill = "grey", colour = "grey", size = 0.1, show.legend = FALSE) +
  geom_point(data = site_list_sub, aes(x = lon, y = lat), alpha = 0.8, size = 3) +
  geom_point(data = site_pixels, aes(x = lon, y = lat), colour = "white", shape = 0, alpha = 0.8, size = 2.1) +
  # geom_rect(data = bbox, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), 
  #           alpha = 0.4, colour = "red", size = 0.1, linetype = 1) +
  # scale_x_continuous(limits = sa_lons, expand = c(0, 0), breaks = seq(15, 35, 5)) +
  # scale_y_continuous(limits = sa_lats, expand = c(0, 0), breaks = seq(-35, -30, 5)) +
  scale_fill_viridis(
    option = "magma",
    name = "Temperature (°C)",
    alpha = 0.8) +
  #scale_fill_viridis(limits = limits, expression(paste("Temperature (°C)"))) +
  xlab("") + ylab("") +
  annotate("text", label = "INDIAN\nOCEAN", x = 32.00, y = -35.0,
             size = 5, angle = 0, colour = "black") +
    annotate("text", label = "ATLANTIC\nOCEAN", x = 17.00, y = -35.0,
             size = 5, angle = 0, colour = "black") +
    annotate("text", label = "Benguela", x = 16.0, y = -31.7,
             size = 6, angle = 302, colour = "black") +
    annotate("text", label = "Agulhas", x = 31.7, y = -31.7,
             size = 6, angle = 50, colour = "black") +
  guides(fill = guide_colourbar()) +
  scale_x_continuous(expand = c(0, 0),
                       labels = scales::unit_format(unit = "°E", sep = "")) +
    scale_y_continuous(expand = c(0, 0),
                       labels = scales::unit_format(unit = "°S", sep = "")) +
  theme(panel.background = element_rect(fill = "ivory", colour = NA),
        panel.border = element_rect(colour = "black", size = 0.5),
        panel.grid.minor = element_line(colour = "NA"),
        panel.grid.major = element_line(colour = "ivory", size = 0.2, linetype = "dotted"),
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 8),
        legend.key = element_blank(),
        legend.background = element_blank(),
        axis.ticks = element_line(size = 0.5))
site_map

# png("Figures/site_map.png", width = 8, height = 5, pointsize = 6)
```

@@

# load("Data_P1/insitu_wind.RData")
# 
# test1 <- insitu_wind %>% 
#   mutate(lat = case_when(site == "Port Nolloth" ~ "-29.25241",
#                                     site == "Saldanha Bay" ~ "-33.01054",
#                                     site  == "Yzerfontein" ~ "-33.36068",
#                                     site  == "Kommetjie" ~ "-34.13667",
#                                     site  == "Lamberts Bay" ~ "-32.09185",
#                                     site  == "Sea Point" ~ "-33.91847"))
# 
# test <- test1 %>% 
#   mutate(lon = case_when(site == "Port Nolloth" ~ "16.86710",
#                                     site == "Saldanha Bay" ~ "17.95063",
#                                     site  == "Yzerfontein" ~ "18.15731",
#                                     site  == "Kommetjie" ~ "18.32674",
#                                     site  == "Lamberts Bay" ~ "18.30262",
#                                     site  == "Sea Point" ~ "18.38217"))
# 
# test_final <- test %>% 
#   select(date,lat,lon,dir_circ, mean_speed) %>% 
#   dplyr::rename(speed = mean_speed) %>% 
#   dplyr::rename(dir = dir_circ)

@@

```{r}
# load("Data_P1/SACTN_overlap.RData")
# load("Data_P1/wind_daily.RData")
# wind_daily <- wind_daily%>% 
#   dplyr::rename(site = temp_sites) # Renaming to match the `match_func` previously created
# 
# insitu_wind <- match_func(df = wind_daily)  # Using `match_func`
# 
# insitu_wind <- insitu_wind %>% 
#   filter(year(date) %in% seq(2010, 2014)) # The years 2010-2014 is the years of interest and the years for which wavelets are/will be created.

@@

insitu_wind <- insitu_wind %>% 
  drop_na()

wave_daily_renamed <- insitu_wind %>% 
  dplyr::rename(spd = mean_speed) %>%
  dplyr::rename(dir = dir_circ) 
source("functions/wind.rose.R")
p.wr2 <- plot.windrose(data = wave_daily_renamed,
              spd = "spd",
              dir = "dir")
p.wr3 <- p.wr2 + facet_wrap(.~ site, ncol = 2, nrow = "") +
  theme(strip.text.x = element_text(size = 25))
p.wr3 # RWS: You'll want to remove the NA part in the figure output

#########################
library(openair)
print(
with(insitu_wind,
     windRose(data_frame(ws=mean_speed, wd=dir_circ, 
                         date=date, station=factor(site)),

              paddle=FALSE, type="station", width=2))
)
png("Figures/wind.png", width = 8, height = 5, pointsize = 6)
?windRose
# insitu_wind_2 <- insitu_wind %>% 
#   filter(site == "Port Nolloth")
# 
# insitu_wind_3 <- insitu_wind %>% 
#   filter(site == "Lamberts Bay")
# 
# plotPN <- plot(as.factor(format(insitu_wind_2$date, "%Y-%m")), insitu_wind_2$insitu_temp, col = "lightpink")
# plotLB <- plot(as.factor(format(insitu_wind_3$date, "%Y-%m")), insitu_wind_3$insitu_temp, col = "lightpink")
#        
# ?plot
```

@@

# MODIS_Chloro <- "~/Documents/Masters_2019/MastersProject/Data"
# MODIS_Chloro <- fread(paste0(MODIS_Chloro, "/BC-M ODIS.Aqua.L3m_8D_CHL_chlor_a_9km-2002185-2018345.csv"),
#             col.names = c("lon", "lat", "chloro", "date"))

@@

Here I want to test using generalised linear hypotheses if there is a difference in the intensity of upwellling events between the insitu and satellite data.
Do the in situ and satelllite derived data yield the same number of events.

library(multcomp) # for generalized linear hypothesis test (glht)

Determining the R2 value between *in situ* and remotely sensed SST

```{r}
# Load time series for both datasets
load("prep/SA_coastal_temps.RData")
SA_coastal_temps$date <- as.Date(SA_coastal_temps$date)
load("data/OISSTdaily.Rdata")

resultsR2 <- data.frame()
for(i in 1:length(levels(SA_coastal_temps$site))) {
  x <- subset(SA_coastal_temps, site == levels(SA_coastal_temps$site)[i])
  y <- subset(OISSTdaily, site == levels(SA_coastal_temps$site)[i])
  x <- x[x$date %in% y$date,]
  y <- y[y$date %in% x$date,]
  z <- data.frame(site = as.character(x$site[1]), R2 = round(coef(lm(y$temp~x$temp))[2],2))
  resultsR2 <- rbind(resultsR2, z)
}

# Add column for plotting
row.names(resultsR2) <- NULL
resultsR2$R22 <- paste0("R^2 ==", format(resultsR2$R2, digits=2))
```

```{r}
# Loading the *in situ* and Remotely sensed SST

load("Data_P1/SACTN_fyears.RData")
load("Data_P1/MUR_fyears.RData")
load("Data_P1/OISST_fyears.RData")
load("Data_P1/G1SST_fyears.RData")
load("Data_P1/K10_fyears.RData")

R2 <- data.frame()
for(i in 1:length(levels(SACTN_fyears$site))) {
  x <- subset(SACTN_fyears, site == levels(SACTN_fyears$site)[i])
  y <- subset(OISST_fyears, site == levels(OISST_fyears$site)[i])
  x <- x[x$date %in% y$date,]
  y <- y[y$date %in% x$date,]
  z <- data.frame(site = as.character(x$site[1]), R2 = coef(lm(y$temp~x$temp))[2],na.action=na.exclude)
  R2 <- rbind(R2, z)
}
```

@@

```{r} 
PCA_1 <- rda(tester)
summary(PCA)

@@

Mond:
- Try PCA
- map it/plot
- dave upwelling index

Tuesday
- Do exercises
